Figures

### 2019-05-10 figures/06_lulc_buffer_demo.Rmd
towards a CDL demo

>>>>

```{r cdl_viewport}
library(raster)
library(dplyr)

cdl_key <- read.csv("../data/cdl/cdl_key.csv", stringsAsFactors = FALSE)

r  <- raster::raster("../data/cdl/2745.tif")

cdl_table <- as.data.frame(table(values(r)), stringsAsFactors = FALSE) %>%
    mutate(code = as.integer(Var1)) %>%
    dplyr::select(-Var1) %>%
    left_join(cdl_key, by = "code")

test2 <- cdl_table %>% 
  dplyr::filter(description != "Background") %>%
  rename(n = Freq) %>%
  arrange(desc(n)) %>%
  group_by(category) %>%
  summarize(group_n = sum(n, na.rm = TRUE), is_ag = first(is_ag)) %>%
  ungroup() %>%
  mutate(percent = round((group_n / sum(group_n, na.rm = TRUE)) * 100, 0)) %>%
  dplyr::filter(percent >= 1) %>%
  arrange(is_ag, percent) 
%>%
  add_row(category = "ag", group_n = 100, is_ag = "ag", percent = 200)

test2 <- test2 %>%
  add_row(category = "ag", group_n = NA, is_ag = NA, percent = 
            sum(dplyr::filter(test2, is_ag == "ag" & 
                                category != "pasture")$percent))

ggplot() + 
  geom_col(data = test2, aes(x = category, 
                             y = percent, 
                             fill = category)) +
  theme(legend.direction = "horizontal", 
        legend.position = 0,
        axis.text.x = element_text(angle = 90)) +
  guides(fill = guide_legend(ncol = 2)) +
  ggtitle("CDL llid = 2745")
```
